A practical look at genetic algorithms

### 2015-11-28 evolutionaryComputation/practicals/report.tex
forgot to add the original uml
Added a bunch of uml

\documentclass{article}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{tikz-uml}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{svg}
\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

\newcommand{\brcell}[2][l]{%
	\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
\begin{document}
\author{Jappie Klooster}
\title{A practical look at genetic algorithms}
\maketitle

@@

\subsection{Architecture}
The architecture was created incrementally, I just implemented the functions
without thinking much about how to combine them.  I first started with the
fittest functions. Then I went on with selection, and finally I did the
crossover.

@@

\section{Conclusion}
%What did I learn from my observation?
\end{document}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsRule{*}{mps}{*}{}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{emp}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{svg}
\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

\newcommand{\brcell}[2][l]{%
	\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
\begin{document}
\begin{empfile}
\begin{empcmds}
input metauml;
\end{empcmds}
\author{Jappie Klooster}
\title{A practical look at genetic algorithms}
\maketitle

@@

\subsection{Architecture}
\begin{figure}[ht!]
\centering
\begin{emp}[classdiag](20,20)
Class.mem("Member")("+Fitness:Int", "+genes:String")();
Class.pop("Population")("+members:Seq[Member]", "+factory:String=>Member")();
Class.pairedPop("PairedPopulation")("+members:Seq[Pair]","+factory:String=>Member")(
"+pairedToPop(how):Population");
Class.pai("Pair")("+father:Member","+mother:Member")();

leftToRight.top(20)(pop,pairedPop);
topToBottom.left(60)(pop,mem);
leftToRight.top(80)(mem, pai);

drawObjects(mem,pop,pairedPop,pai);
link(association)(pai.n -- pairedPop.s);
item(iAssoc)("*")(obj.se = pai.n);
link(association)(mem.e -- pai.w);
item(iAssoc)("2")(obj.sw = mem.e);

link(association)(mem.n -- pop.s);
item(iAssoc)("*")(obj.se = mem.n);
\end{emp}
\caption{Case classes}
\end{figure}

\begin{figure}[ht!]
\centering
\begin{emp}[classdiag](20,20)
Class.evo("Evolution")(
"+valuation: FitnessEvaluator",
"mateSelector:IMateSelector",
"offSpringGenerator: PairedPopulation => Population",
"fittestFilter: (Population, Population) => Population",
"hasGoodEnoughSolution: Population => Boolean")(
"startGenetic(seed:Population): Seq[Population]",
"genetic(prev:Seq[Population]): Seq[Population]",
"step(parents:Population): Population",
);
Instance.fit("Fitness")(
	"uniformlyScaled()",
	"linearlyScaled()",
	"blockValuation(block:Seq[Float])"
);
Instance.filt("FittestFilter")(
	"killParents()",
	"truncateElitism()",
	"tournementElitism()"
	);
Instance.select("MateSelection")(
	"tournementSelect()"
);
Instance.factor("MemberFactories")(
	"tightlyLinkded()",
	"randomlyLinked()",
	"withCoinflipMutation(function):function",
);
Instance.off("OffspringGenerator")(
	"uniformCross()",
	"singlePointCross()",
	"twoPointCross()"
);

topToBottom.left(20)(evo,fit,filt,factor);
leftToRight.top(20)(fit,off);
leftToRight.top(20)(filt,select);

drawObjects(evo,fit,factor,filt,select,off);
\end{emp}
\caption{Algoritm}
\end{figure}

\begin{figure}[ht!]
\centering
\begin{emp}[classdiag](20,20)
Class.ex("Experiment")(
	"+name:String",
	"+variation:String",
	"evolution: Evolution",
	"factory:String => IMember"
)();
Class.result("RunResult")(
	"popSize:Int",
	"success:Boolean",
	"runtime:Long",
	"generationCount:Int",
	"fitnessCallCount:Int"
	)();
Class.stoastic("StoasticRun")(
	"runs:Seq[RunResult]",
	"required:Int",
	)();
topToBottom.left(20)(ex,result,stoastic);
drawObjects(ex,result,stoastic);
\end{emp}
\caption{Experiment}
\end{figure}

\clearpage
The architecture was created incrementally, I just implemented the functions
without thinking much about how to combine them.  I first started with the
fittest functions. Then I went on with selection, and finally I did the
crossover.

@@

\section{Conclusion}
%What did I learn from my observation?
\end{empfile}
\end{document}
